Space-time plots

### 2017-04-05 Rmd/space-time.Rmd
Initial steps in revision of analysis, including updated calibration and main data sets (addition of new effective extent variable, change of variable names:
sampled_area -> act_ext
eff_ext
study_duration -> act_dur
eff_dur
samp_duration -> samp_dur

Analyses revised through calibration set and data merging of main analysis

p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data/result")
p_calib <- full_path(p_root, "external/data/calibration")
# dat <- as.data.table(read_excel(full_path(p_dat, "merged.xlsx")))
dat <- as.data.table(read_excel(full_path(p_dat, "mergedfff.xlsx")))
cal <- data.table(read_excel(fp(p_calib, "merged_calibrationffff.xlsx")))
full <- data.table(read_excel(fp(p_dat, "full_less_Treuer.xlsx")))

setnames(dat, "DOI/title", "DOI")
dat[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dat[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
full <- gsub("DOI:|doi:|DOI: |doi: |DOI ", "", full$DOI)
full <- gsub("\\s", "", full)  # remove DOI and whitespace
unique(full)

dat <- dat[, names(dat)[1:20], with = FALSE]

unique(dat$study_type)
dat[, study_type := tolower(study_type)]
kwords <- c("field", "paleo", "remote", "automated", "other")
for(i in 1:length(kwords)) dat[like(study_type, kwords[i]), st := i]

@@

# class(cal$DOI)
# class(dat$DOI)
# unique(cal$DOI) %in% unique(dat$DOI)
# match(cal$DOI, dat$DOI)
# match(dat$DOI, cal$DOI)
# dat[dat$DOI %in% cal$DOI, DOI]
# dat[cal$DOI %in% dat$DOI, ]
# cal[DOI == dat[cal$DOI %in% dat$DOI, DOI][11]]
# dat[DOI == dat[cal$DOI %in% dat$DOI, DOI][7]]

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
dat2 <- copy(dat[, .(st, DOI, study_type, plot_res, n_sites, sampled_area,
                     samp_duration, t_btwn_samp, study_duration)])
rnms <- c("st", "DOI", "study_type", "feature", "observer", "plot_res", 
          "n_sites", "sampled_area", "t_btwn_samp", "study_duration")
calr <- cal[, rnms, with = FALSE]
for(j in names(calr)[c(4, 6:10)]) set(calr, j=j, value = as.numeric(calr[[j]]))

# select down to columns of interest
# st <- calr$study_type[which(calr$feature != 99)]
calr <- calr[feature != 99, lapply(.SD, mean), by = .(DOI, feature), 
             .SDcols = rnms[c(1, 6:10)]]
length(unique(calr$DOI)) + length(unique(dat$DOI))  # 140 papers providing dat
unique(calr$DOI)
calr_type <- data.table(cbind("DOI" = unique(calr$DOI), # calib field studies
                              "study_type" = c(rep("field", 5), "paleo",
                                               rep("field", 4))))

# combine full and calibration
calr[, samp_duration := NA]
calr[, "feature" := NULL] #c("DOI", "feature") := NULL]
calr <- merge(calr, calr_type, by = "DOI")
setcolorder(calr, names(calr)[c(2:1, 9, 3:5, 8, 6:7)])
datf <- rbind(cbind("dsrc" = 1, dat2), cbind("dsrc" = 2, calr))
doisup <- c(unique(cal$DOI_data_source), unique(dat$DOI_data_source))
doisup <- doisup[!is.na(doisup) & doisup != "NA" & doisup != "-"]
doisup <- unlist(strsplit(doisup, ";"))

@@

`r length(unique(full)) + 20 + 57` papers main analysis (everyone's but Tim's)

`r (length(unique(full)) + 20 + 57) / 42918 * 100` % of all papers since 2004

@@

### Adjustments/fixes
1. if `samp_duration != study_duration` and `t_btwn_samp == 0`, set `study_duration == samp_duration` (actually, no, in many cases there is a good reason to have to `study_duration != samp_duration` (see below))
2. Prior to scaling the data in log10 space, we need to make one adjustment. Time between samples has many 0 values because many observations are simply one-offs.  Set these to an arbitrarily large value which will represent clear separation on axis from high frequency studies. A function is defined here for this purpose, and will be applied after bootstrapping is done.

```{r, message=FALSE, warning=FALSE, results='hide'}
# apply fixes (mostly to account for observer omissions)
# 1. if samp_duration != study_duration and t_btwn_samp == 0, set 
#    study_duration == samp_duration
names(datf)
datf[t_btwn_samp == 0 & (study_duration != samp_duration), ]  
dat[t_btwn_samp == 0 & (study_duration != samp_duration), c(1, 3, 8:13), with=F]  
# function to set t_btwn_samp to 365 * 100000 to indicate once-off studies 
# when t_btwn_samp == 0.  
to_infin_byond <- function(tbtwn) ifelse(tbtwn == 0, 365 * 10000, tbtwn)

@@

Defined by the per variable CV based on uncertainty between observers. Here we are just going to use apply the variability to each variable for every observation (previous incarnation used uncertainty on just the variables listed as uncertain, with recalculation of dependent variables (`study_duration`, `sampled_area`) made after pertubation [see commit prior to second or third commit on 4 April for code]).

@@

    dnew <- copy(datf[, .(plot_res, sampled_area, t_btwn_samp, study_duration)])
    # modifiers
    modvec <- sapply(p, function(y) {
      mv <- runif(nrow(dnew), min = 1 - y, max = 1 + y)
      mv
    })

    for(j in 1:ncol(modvec)) set(dnew, j = j, value = dnew[[j]] * modvec[, j])
    dnew[plot_res <= 0, plot_res := 0.00000001]
    dnew[sampled_area <= 0, sampled_area := 0.00000001]
    dnew[study_duration <= 0, study_duration := 0.00000001]
    dnew[t_btwn_samp < 0, t_btwn_samp := 0.00000001]

@@

```{r, eval=FALSE}
length(which(datf$study_type %in% 
               c("remote sensing", "other geographic data"))) / nrow(datf)
datf[t_btwn_samp == 0, .N] / datf[, .N]  # 36% of samples are once-offs
datf[study_duration == samp_duration, .N] / nrow(datf)
datf[(study_duration == samp_duration) & t_btwn_samp != 0]
datf[(study_duration != samp_duration) & t_btwn_samp == 0]

hdat <- cbind("res" = log10(datf$plot_res), "ext" = log10(datf$sampled_area), 
              "int" = log10(to_infin_byond(datf$t_btwn_samp)), 
              "dur" = log10(datf$study_duration))
hdat <- data.table(hdat)
# set bounds for histograms
hdat[res < aaxis1$logres[1], res := aaxis1$logres[1]]
hdat[res > ry[2], res := ry[2]]
hdat[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)

@@

vs <- c("res", "ext", "int", "dur")
hdat_bs <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  print(x)
  DT <- bootperturb[[x]]
  hdb <- cbind("res" = log10(DT$plot_res), "ext" = log10(DT$sampled_area), 
               "int" = log10(to_infin_byond(DT$t_btwn_samp)), 
               "dur" = log10(DT$study_duration))
  hdb <- data.table(hdb)
  hdb[res < aaxis1$logres[1], res := aaxis1$logres[1]]
  hdb[res > ry[2], res := ry[2]]
  hdb[, lapply(.SD, range)]
  hdb[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)
  hists <- lapply(1:length(vs), function(y) {  # y <- 2
    #print(y)
    hdbv <- hdb[[vs[y]]]
    hbrks <- brksl[[y]]
    hdbv[hdbv < hbrks[1]] <- hbrks[1]
    hdbv[hdbv > hbrks[length(hbrks)]] <- hbrks[length(hbrks)]
    h <- hist(hdbv, breaks = hbrks, plot = FALSE)
    h$density <- h$counts / sum(h$counts) * 100
    h
  })
})

@@

# datf[, plot(log10(n_sites), log10(plot_res))]
# dat[like(study_type, "field"), plot(log10(n_sites), log10(plot_res))]
datf[like(study_type, "field"), plot(log10(plot_res), log10(sampled_area), 
                                     ylim = c(-10, 10))]

datf[like(study_type, "remote"), 
     points(log10(plot_res), log10(sampled_area), pch = 20, col = "red")]
datf[like(study_type, "automated"), 
     points(log10(plot_res), log10(sampled_area), pch = 20, col = "blue")]
lines(aaxis1$logres, aaxis2$logarea[-16] )
datf[, .N / nrow(datf) * 100, by = st]

datf[, plot(log10(t_btwn_samp), log10(study_duration), pch = 20)]
datf[which(hdat[[3]] < -1.380211), 
     points(log10(t_btwn_samp), log10(study_duration), pch = 20, col = "blue")]
datf[like(study_type, "automated"), 
     points(log10(t_btwn_samp), log10(study_duration), pch = 20, col = "red")]

@@

# extent
extdat3 <- data.table(x = log10(kdat$study_duration), 
                      y = log10(kdat$sampled_area))
extdat3$n <- rep(1, nrow(extdat3))
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56)#ceiling(ex[2]))
extdat3[x < ex[1], x := ex[1]]
extdat3[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat3[y < ey[1], y := ey[1]]
extdat3[y > ey[2], y := ey[2]]
coordinates(extdat3) <- ~x + y

# temporal framing
tempdat <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$study_duration))
tempdat <- tempdat[round(x, 8) != 6.56229286, ]  # remove one-time observations
tempdat$n <- rep(1, nrow(tempdat))
tx <- range(tempdat$x)
tx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
#tx[2] <- 6.56
tx[2] <- 5.57
tempdat[x < rx[1], x := rx[1]]
tempdat[x > rx[2], x := rx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ty[1]), 5.56)#ceiling(ex[2]))
tempdat[y < ty[1], y := ty[1]]
tempdat[y > ty[2], y := ty[2]]
coordinates(tempdat) <- ~x + y

# spatial framing
spatdat <- data.table(x = log10(kdat$plot_res), y = log10(kdat$sampled_area))
spatdat$n <- rep(1, nrow(spatdat))
sx <- range(aaxis1$logres)
sx[1] <- -5  # set limits to 0.01 cm^2
spatdat[x < sx[1], y := sx[1]]
spatdat[x > sx[2], y := sx[2]]
sy <- range(aaxis2$logarea)
spatdat[y < sy[1], y := sy[1]]
spatdat[y > sy[2], y := sy[2]]
coordinates(spatdat) <- ~x + y

@@

# datf[, plot(log10(study_duration), log10(sampled_area), xlim)]

@@

+ If `plot_res` and/or `n_sites` uncertain, then `sampled_area` must be. Recalculate using random draw within the uncertain variable 
+ If `t_btwn_samp` and/or `samp_duration` uncertain, do the same as above, but we have no variable for n repeats for calculating `study_duration`.

```{r}
svars <- c("plot_res", "n_sites", "sampled_area", "samp_duration",
           "t_btwn_samp", "study_duration")

@@

# 1. if samp_duration OR t_btwn_samp is uncertain, study_duration must also be. 
id <- which((senst$sampd == 1 | senst$tbtwn == 1) & senst$studyd == 0)
senst[id, "studyd"] <- 1

# 2. if study_duration is uncertain but t_btwn and samp_duration are not, treat
# both as uncertain
# although it is possible that just n_repeats is uncertain, but more likely 
# that observers didn't note this is sensitive. 
id <- which(senst$tbtwn == 0 & senst$sampd == 0 & senst$studyd == 1)
senst[id, c("sampd", "tbtwn")] <- 1

# 3. if plot_res or n_sites is uncertain, then sampled_area must be
id <- which((senst$res == 1 | senst$n == 1) & senst$sarea == 0)
senst[id, "sarea"] <- 1

@@

```{r, eval = FALSE, echo = FALSE}
### Bootstrapping
# Good old-fashioned bootstrapping with replacement, no perturbation of value
# bootstrap
set.seed(1)
bootsamp <- lapply(1:1000, function(x) {
  if((x / 100) %in% 1:100) print(x)
  dnew <- copy(datf[, .(plot_res, sampled_area, t_btwn_samp, study_duration)])
  dnew <- dnew[sample(1:.N, size = .N, replace = TRUE), ]
  dnew[, t_btwn_samp := to_infin_byond(t_btwn_samp)]  # set high
  dnew
})

@@

# extent
extdat2 <- data.table(x = log10(bootdt$study_duration), 
                      y = log10(bootdt$sampled_area))
extdat2$n <- rep(1, nrow(extdat2))
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56)#ceiling(ex[2]))
extdat2[x < ex[1], x := ex[1]]
extdat2[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat2[y < ey[1], y := ey[1]]
extdat2[y > ey[2], y := ey[2]]
coordinates(extdat2) <- ~x + y

@@

# datf[, plot(log10(study_duration), log10(sampled_area), xlim)]
```

@@

tbtwn <- datf$t_btwn_samp
# which(tbtwn < (0.1 / (60 * 60 * 24)) & tbtwn > 0)
tbtwn <- ifelse(tbtwn == 0, 0.1 / (60 * 60 * 24), tbtwn)
tempdat2 <- data.table(x = log10(tbtwn), y = log10(datf$study_duration))
tempdat2[x == min(x), x := -5.5]
tempdat2[x > -5.5 & x < tx[1], x := tx[1]]
# tempdat2[y == min(y)]
tempdat2[y > ty[2], y := ty[2]]
tx2 <- round(range(tempdat2$x), 1)
ty2 <- round(range(tempdat2$y), 1)

# tempdat2 <- data.table(x = log10(to_infin_byond(datf$t_btwn_samp)), 
#                       y = log10(datf$study_duration))
spatdat2 <- data.table(x = log10(datf$plot_res / 10000), # convert to ha
                       y = log10(datf$sampled_area))
sx2 <- round(range(spatdat2$x), 1)
sx2[2] <- 4.8
sy2 <- round(range(spatdat2$y), 1)

>>>>

p_root <- set_base_path("ecoscales")
p_dat <- full_path(p_root, "external/data/result")
p_calib <- full_path(p_root, "external/data/calibration")
# dat <- as.data.table(read_excel(full_path(p_dat, "merged.xlsx")))
dat <- as.data.table(read_excel(full_path(p_dat, "mergedfffff.xlsx")))
dato <- as.data.table(read_excel(full_path(p_dat, "archive/mergedfff.xlsx")))
cal <- data.table(read_excel(fp(p_calib, "merged_calibrationfffff.xlsx")))
full <- data.table(read_excel(fp(p_dat, "full_no_treuer_toss.xlsx")))
# full <- data.table(read_excel(fp(p_dat, "full_less_Treuer.xlsx")))

setnames(dato, "DOI/title", "DOI")
dato[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dato[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace

setnames(dat, "DOI/title", "DOI")
dat[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
dat[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
cal[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
full <- gsub("DOI:|doi:|DOI: |doi: |DOI ", "", full$DOI)
full <- gsub("\\s", "", full)  # remove DOI and whitespace

# subset main results and define study type
dat <- dat[, names(dat)[1:22], with = FALSE]
dat[, study_type := tolower(study_type)]
# kwords <- c("field", "paleo", "remote", "automated", "other")
tst <- dat[, study_type]

kwords <- cbind(c("field", "paleo", "remote", "automated", "other"), 
                c("field", "paleo", "remote", "automated", "other"))
# for(i in 1:length(kwords)) dat[like(study_type, kwords[i]), st := i]
for(i in 1:nrow(kwords)) {
  dat[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}
# cbind(tst, dat[, study_type])

@@

kwords <- cbind(c("field", "direct", "paleo", "remote", "automated", "other"),
                c("field", "field", "paleo", "remote", "automated", "other"))
cal[, study_type := tolower(study_type)]
tst <- cal[, study_type]
for(i in 1:nrow(kwords)) {
  cal[like(study_type, kwords[i, 1]), study_type := kwords[i, 2]]
}
# cbind(tst, cal[, study_type])

# unique(dat$DOI)
# a <- unique(dato$DOI)
# b <- unique(dat$DOI)
# notin <- sort(a)[!sort(a) %in% sort(b)]
# dato[DOI %in% notin, 1:5, with = FALSE]
# dat[observer == "Ahmed" & journal == "Oecologia"]
# unique(cal$DOI) %in% unique(dat$DOI)
# match(cal$DOI, dat$DOI)
# match(dat$DOI, cal$DOI)
# dat[dat$DOI %in% cal$DOI, DOI]
# dat[cal$DOI %in% dat$DOI, ]
# cal[DOI == dat[cal$DOI %in% dat$DOI, DOI][11]]
# dat[DOI == dat[cal$DOI %in% dat$DOI, DOI][7]]
# dat[observer == "Treuer", unique(DOI)]  # 19

@@

## Data prep
### Merge full and calibration datasets
```{r, message=FALSE, warning=FALSE, results='hide'}
# dat2 <- copy(dat[, .(st, DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
#                      samp_dur, t_btwn_samp, act_dur, eff_dur)])
# rnms <- c("st", "DOI", "study_type", "feature", "observer", "plot_res", 
#           "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
#           "act_dur", "eff_dur")
dat2 <- copy(dat[, .(DOI, study_type, plot_res, n_sites, act_ext, eff_ext,
                     samp_dur, t_btwn_samp, act_dur, eff_dur)])
rnms <- c("DOI", "study_type", "feature", "observer", "plot_res", 
          "n_sites", "act_ext", "eff_ext", "samp_dur", "t_btwn_samp",
          "act_dur", "eff_dur")
calr <- cal[, rnms, with = FALSE]
selind <- c(3, 5:length(rnms))
for(j in names(calr)[selind]) set(calr, j=j, value = as.numeric(calr[[j]]))

# str(calr)
# select down to columns of interest
# st <- calr$study_type[which(calr$feature != 99)]
calr_type <- calr[feature != 99, { 
  list(unique(study_type[!is.na(study_type)]))
}, by = .(DOI, feature)][, list("study_type" = unique(V1)), by = DOI]

# calr[DOI == "10.1007/s00442-005-0338-3" & feature == 2, 
#      mean(eff_dur, na.rm = T)]
calr <- calr[feature != 99, {
  lapply(.SD, function(x) mean(x, na.rm = TRUE))
},  by = .(DOI, feature), .SDcols = rnms[c(5:ncol(calr))]]
length(unique(calr$DOI)) + length(unique(dat$DOI))  # 134 papers providing dat
# unique(calr$DOI)

# calr_type <- data.table(cbind("DOI" = unique(calr$DOI), # calib field studies
#                               "study_type" = c(rep("field", 5), "paleo",
#                                                rep("field", 4))))

# combine full and calibration
# calr[, samp_dur := NA]
calr[, samp_dur := NA]
calr[, "feature" := NULL] #c("DOI", "feature") := NULL]
calr <- merge(calr, calr_type, by = "DOI")
setcolorder(calr, names(dat2))
datf <- rbind(cbind("dsrc" = 1, dat2), cbind("dsrc" = 2, calr))
doisup <- c(unique(cal$DOI_data_source), unique(dat$DOI_data_source))
doisup <- doisup[!is.na(doisup) & doisup != "NA" & doisup != "-"]
doisup <- unlist(strsplit(doisup, ";"))
```

@@

`r length(unique(full)) + (57 - 19)` papers main analysis (adding in Tim's rejected number separately)

`r (length(unique(full)) + (57 - 19)) / 42918 * 100` % of all papers since 2004

@@

### Adjustments/fixes
1. if `samp_dur != act_dur` and `t_btwn_samp == 0`, set `act_dur == samp_dur` (actually, no, in many cases there is a good reason to have to `act_dur != samp_dur` (see below))
2. Prior to scaling the data in log10 space, we need to make one adjustment. Time between samples has many 0 values because many observations are simply one-offs.  Set these to an arbitrarily large value which will represent clear separation on axis from high frequency studies. A function is defined here for this purpose, and will be applied after bootstrapping is done.

```{r, message=FALSE, warning=FALSE, results='hide'}
# apply fixes (mostly to account for observer omissions)
# 1. if samp_dur != act_dur and t_btwn_samp == 0, set 
#    act_dur == samp_dur
names(datf)
datf[t_btwn_samp == 0 & (act_dur != samp_dur), ]  
dat[t_btwn_samp == 0 & (act_dur != samp_dur), c(1, 3, 8:13), with=F]  
# function to set t_btwn_samp to 365 * 100000 to indicate once-off studies 
# when t_btwn_samp == 0.  
to_infin_byond <- function(tbtwn) ifelse(tbtwn == 0, 365 * 10000, tbtwn)

@@

Defined by the per variable CV based on uncertainty between observers. Here we are just going to use apply the variability to each variable for every observation (previous incarnation used uncertainty on just the variables listed as uncertain, with recalculation of dependent variables (`act_dur`, `act_ext`) made after pertubation [see commit prior to second or third commit on 4 April for code]).

@@

    dnew <- copy(datf[, .(plot_res, act_ext, t_btwn_samp, act_dur)])
    # modifiers
    modvec <- sapply(p, function(y) {
      mv <- runif(nrow(dnew), min = 1 - y, max = 1 + y)
      mv
    })

    for(j in 1:ncol(modvec)) set(dnew, j = j, value = dnew[[j]] * modvec[, j])
    dnew[plot_res <= 0, plot_res := 0.00000001]
    dnew[act_ext <= 0, act_ext := 0.00000001]
    dnew[act_dur <= 0, act_dur := 0.00000001]
    dnew[t_btwn_samp < 0, t_btwn_samp := 0.00000001]

@@

```{r, eval=FALSE}
length(which(datf$study_type %in% 
               c("remote sensing", "other geographic data"))) / nrow(datf)
datf[t_btwn_samp == 0, .N] / datf[, .N]  # 36% of samples are once-offs
datf[act_dur == samp_dur, .N] / nrow(datf)
datf[(act_dur == samp_dur) & t_btwn_samp != 0]
datf[(act_dur != samp_dur) & t_btwn_samp == 0]

hdat <- cbind("res" = log10(datf$plot_res), "ext" = log10(datf$act_ext), 
              "int" = log10(to_infin_byond(datf$t_btwn_samp)), 
              "dur" = log10(datf$act_dur))
hdat <- data.table(hdat)
# set bounds for histograms
hdat[res < aaxis1$logres[1], res := aaxis1$logres[1]]
hdat[res > ry[2], res := ry[2]]
hdat[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)

@@

vs <- c("res", "ext", "int", "dur")
hdat_bs <- lapply(1:length(bootperturb), function(x) {  # x <- 1
  print(x)
  DT <- bootperturb[[x]]
  hdb <- cbind("res" = log10(DT$plot_res), "ext" = log10(DT$act_ext), 
               "int" = log10(to_infin_byond(DT$t_btwn_samp)), 
               "dur" = log10(DT$act_dur))
  hdb <- data.table(hdb)
  hdb[res < aaxis1$logres[1], res := aaxis1$logres[1]]
  hdb[res > ry[2], res := ry[2]]
  hdb[, lapply(.SD, range)]
  hdb[ext < -6, ext := -6]  # set minimum extent -6 (0.01 m2)
  hists <- lapply(1:length(vs), function(y) {  # y <- 2
    #print(y)
    hdbv <- hdb[[vs[y]]]
    hbrks <- brksl[[y]]
    hdbv[hdbv < hbrks[1]] <- hbrks[1]
    hdbv[hdbv > hbrks[length(hbrks)]] <- hbrks[length(hbrks)]
    h <- hist(hdbv, breaks = hbrks, plot = FALSE)
    h$density <- h$counts / sum(h$counts) * 100
    h
  })
})

@@

# datf[, plot(log10(n_sites), log10(plot_res))]
# dat[like(study_type, "field"), plot(log10(n_sites), log10(plot_res))]
datf[like(study_type, "field"), plot(log10(plot_res), log10(act_ext), 
                                     ylim = c(-10, 10))]

datf[like(study_type, "remote"), 
     points(log10(plot_res), log10(act_ext), pch = 20, col = "red")]
datf[like(study_type, "automated"), 
     points(log10(plot_res), log10(act_ext), pch = 20, col = "blue")]
lines(aaxis1$logres, aaxis2$logarea[-16] )
datf[, .N / nrow(datf) * 100, by = st]

datf[, plot(log10(t_btwn_samp), log10(act_dur), pch = 20)]
datf[which(hdat[[3]] < -1.380211), 
     points(log10(t_btwn_samp), log10(act_dur), pch = 20, col = "blue")]
datf[like(study_type, "automated"), 
     points(log10(t_btwn_samp), log10(act_dur), pch = 20, col = "red")]

@@

# extent
extdat3 <- data.table(x = log10(kdat$act_dur), 
                      y = log10(kdat$act_ext))
extdat3$n <- rep(1, nrow(extdat3))
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56)#ceiling(ex[2]))
extdat3[x < ex[1], x := ex[1]]
extdat3[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat3[y < ey[1], y := ey[1]]
extdat3[y > ey[2], y := ey[2]]
coordinates(extdat3) <- ~x + y

# temporal framing
tempdat <- data.table(x = log10(to_infin_byond(kdat$t_btwn_samp)), 
                      y = log10(kdat$act_dur))
tempdat <- tempdat[round(x, 8) != 6.56229286, ]  # remove one-time observations
tempdat$n <- rep(1, nrow(tempdat))
tx <- range(tempdat$x)
tx <- round(rx / 0.5) * 0.5  # round to nearest 0.5
#tx[2] <- 6.56
tx[2] <- 5.57
tempdat[x < rx[1], x := rx[1]]
tempdat[x > rx[2], x := rx[2]]
ty <- range(taxis2$logdays)
ty <- c(floor(ty[1]), 5.56)#ceiling(ex[2]))
tempdat[y < ty[1], y := ty[1]]
tempdat[y > ty[2], y := ty[2]]
coordinates(tempdat) <- ~x + y

# spatial framing
spatdat <- data.table(x = log10(kdat$plot_res), y = log10(kdat$act_ext))
spatdat$n <- rep(1, nrow(spatdat))
sx <- range(aaxis1$logres)
sx[1] <- -5  # set limits to 0.01 cm^2
spatdat[x < sx[1], y := sx[1]]
spatdat[x > sx[2], y := sx[2]]
sy <- range(aaxis2$logarea)
spatdat[y < sy[1], y := sy[1]]
spatdat[y > sy[2], y := sy[2]]
coordinates(spatdat) <- ~x + y

@@

# datf[, plot(log10(act_dur), log10(act_ext), xlim)]

@@

+ If `plot_res` and/or `n_sites` uncertain, then `act_ext` must be. Recalculate using random draw within the uncertain variable 
+ If `t_btwn_samp` and/or `samp_dur` uncertain, do the same as above, but we have no variable for n repeats for calculating `act_dur`.

```{r}
svars <- c("plot_res", "n_sites", "act_ext", "samp_dur",
           "t_btwn_samp", "act_dur")

@@

# 1. if samp_dur OR t_btwn_samp is uncertain, act_dur must also be. 
id <- which((senst$sampd == 1 | senst$tbtwn == 1) & senst$studyd == 0)
senst[id, "studyd"] <- 1

# 2. if act_dur is uncertain but t_btwn and samp_dur are not, treat
# both as uncertain
# although it is possible that just n_repeats is uncertain, but more likely 
# that observers didn't note this is sensitive. 
id <- which(senst$tbtwn == 0 & senst$sampd == 0 & senst$studyd == 1)
senst[id, c("sampd", "tbtwn")] <- 1

# 3. if plot_res or n_sites is uncertain, then act_ext must be
id <- which((senst$res == 1 | senst$n == 1) & senst$sarea == 0)
senst[id, "sarea"] <- 1

@@

```{r, eval = FALSE, echo = FALSE}
### Bootstrapping
# Good old-fashioned bootstrapping with replacement, no perturbation of value
# bootstrap
set.seed(1)
bootsamp <- lapply(1:1000, function(x) {
  if((x / 100) %in% 1:100) print(x)
  dnew <- copy(datf[, .(plot_res, act_ext, t_btwn_samp, act_dur)])
  dnew <- dnew[sample(1:.N, size = .N, replace = TRUE), ]
  dnew[, t_btwn_samp := to_infin_byond(t_btwn_samp)]  # set high
  dnew
})

@@

# extent
extdat2 <- data.table(x = log10(bootdt$act_dur), 
                      y = log10(bootdt$act_ext))
extdat2$n <- rep(1, nrow(extdat2))
ex <- range(taxis2$logdays)
ex <- c(floor(ex[1]), 5.56)#ceiling(ex[2]))
extdat2[x < ex[1], x := ex[1]]
extdat2[x > ex[2], x := ex[2]]
ey <- range(aaxis2$logarea)
extdat2[y < ey[1], y := ey[1]]
extdat2[y > ey[2], y := ey[2]]
coordinates(extdat2) <- ~x + y

@@

# datf[, plot(log10(act_dur), log10(act_ext), xlim)]
```

@@

tbtwn <- datf$t_btwn_samp
# which(tbtwn < (0.1 / (60 * 60 * 24)) & tbtwn > 0)
tbtwn <- ifelse(tbtwn == 0, 0.1 / (60 * 60 * 24), tbtwn)
tempdat2 <- data.table(x = log10(tbtwn), y = log10(datf$act_dur))
tempdat2[x == min(x), x := -5.5]
tempdat2[x > -5.5 & x < tx[1], x := tx[1]]
# tempdat2[y == min(y)]
tempdat2[y > ty[2], y := ty[2]]
tx2 <- round(range(tempdat2$x), 1)
ty2 <- round(range(tempdat2$y), 1)

# tempdat2 <- data.table(x = log10(to_infin_byond(datf$t_btwn_samp)), 
#                       y = log10(datf$act_dur))
spatdat2 <- data.table(x = log10(datf$plot_res / 10000), # convert to ha
                       y = log10(datf$act_ext))
sx2 <- round(range(spatdat2$x), 1)
sx2[2] <- 4.8
sy2 <- round(range(spatdat2$y), 1)
